### 2020-04-23 intro.tex
intro fig

Our analysis focuses on GPU boards that were installed in the second
rework cycle and later, essentially units installed near the beginning
of 2014 and later. Figure~\ref{fig:chronology} is the only one
involving data prior to 2014. All analyses and figures that follow use
only data from 2014 onward. We make the data as well as our analysis
codes to reproduce the graphics available in a public repository (see,
\cite[repository]{repositoryreference}).  While the data is only a 7
MB file, due to the size of Titan it represents over 100,000 years of
GPU operation and may be the largest publicly available GPU
reliability data set. Our hope is that others will use it for
reliability and survival analysis research and go beyond the results
presented here.

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the
data cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A time between failures (TBF) analysis
is given in Sec.~\ref{section:tbf}. Survival analysis based on
Kaplan-Meier modeling (KM) and Cox regression modeling (CR) of
relative hazard rates in various locations are in
Sec.~\ref{section:survival}. A high-level difference between a TBF
analysis and survival analysis (SA) is that TBF studies largely how
GPU reliability affects the machine, wheras SA studies largely how the
machine affects GPU reliability.  Finally, we discuss our main
conclusions and recommendations in Sec.~\ref{section:discussion}.

>>>>

Our analysis focuses on GPU boards that were installed in the second
rework cycle and later, essentially units installed near the beginning
of 2014 and later. Figure~\ref{fig:chronology} is the only one
involving data prior to 2014. All analyses and figures that follow use
only data from 2014 onward. We make the data as well as our analysis R
codes and Python codes to reproduce the graphics in this paper
publicly available (see, \cite[repository to be added in final
version]{repositoryreference,rcodes,pycodes}).  While the data is only
a 7 MB file, due to the size of Titan it represents over 100,000
collective years of GPU operation and may be the largest publicly
available GPU reliability data set. Our hope is that others will use
it for reliability and survival analysis research and go beyond the
results presented here.

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the
data cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A time between failures (TBF) analysis
is given in Sec.~\ref{section:tbf}. Survival analysis based on
Kaplan-Meier modeling (KM) and Cox regression modeling (CR) of
relative hazard rates in various locations are in
Sec.~\ref{section:survival}. The goals of a TBF analysis and of
survival analysis (SA) are different: TBF studies largely how GPU
reliability affects the machine, wheras SA studies largely how the
machine affects GPU reliability.  Finally, we discuss our main
conclusions and recommendations in Sec.~\ref{section:discussion}.
